Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-23 awipev-CO2.Rmd
ESSD: finalize first version time series fig

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("robfilter")) install.packages("robfilter")
if (!require("robfilter")) install.packages("robfilter")
library("robfilter")
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("reshape2")) install.packages("reshape2")
library("reshape2")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("lmtest")) install.packages("lmtest")
library("lmtest")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("seismicRoll")) install.packages("seismicRoll")
library("seismicRoll")
if (!require("scales")) install.packages("scales")
library("scales")
# if (!require("plotly")) install.packages("plotly")
# library(plotly)
if (!require("htmlwidgets")) install.packages("htmlwidgets")
library("htmlwidgets")
if (!require("hms")) install.packages("hms")
library("hms")
knitr::opts_chunk$set(echo = TRUE)

@@

```{r figures for ESSD paper, echo=FALSE, message= FALSE, warning=FALSE}
Mytheme <- function(size_labs = 6, face_font="plain", ...) {
  theme_bw() +
  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
        axis.title.x = element_text(face="bold", size=size_labs, margin=margin(0,0,0,0,"pt")),
        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
        axis.title.y = element_text(face="bold", size=size_labs),
        axis.ticks.x = element_line(size=0.1),
        axis.ticks.y = element_line(size=0.1),
        axis.ticks.length = unit(1.1, "mm"),
        panel.grid.major = element_line(size = 0.25, color="black", linetype="dotted"),
        aspect.ratio = 1 / 3,
        plot.margin = margin(t = 0, r = 1.5, b = 0, l = 1.5, unit = "lines")
  )
}
# select time series data
d <- as_tibble(d_all) %>%
  dplyr::select(datetime, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, ph_dur_corr, at_calc)
# time series temp
ts_temp <- d %>%
  dplyr::filter(!is.na(temp_insitu_11m)) %>% 
ggplot() +
  geom_point(aes(x = datetime, y = temp_insitu_11m), col = "blue", size = 0.15) +
  labs(title = "", x = "Time", y = "In situ temperature (°C)") +
  Mytheme(size_labs = 8)
ggsave(filename = "figures/ts_temp.png")
print(ts_temp) 
# time series sal
ts_sal <- d %>%
  dplyr::filter(!is.na(sal_mix)) %>% 
ggplot() +
  geom_point(aes(x = datetime, y = sal_mix), col = "blue", size = 0.15) +
  labs(title = "", x = "Time", y = "Salinity") +
  Mytheme(size_labs = 8)
ggsave(filename = "figures/ts_sal.png")
print(ts_sal) 
# time series pco2
ts_pco2 <- d %>%
  dplyr::filter(!is.na(pco2_corr)) %>% 
ggplot() +
  geom_point(aes(x = datetime, y = pco2_corr), col = "blue", size = 0.15) +
  labs(title = "", x = "Time", y = expression(paste("C", O[2], " partial pressure (", mu, "atm)"))) +
  Mytheme(size_labs = 8)
ggsave(filename = "figures/ts_pco2.png")
print(ts_pco2) 
# time series pH
ts_ph <- d %>%
  dplyr::select(datetime, pHint_tot_sf, ph_dur_corr) %>%
  dplyr::filter(!is.na(pHint_tot_sf)) %>% 
  pivot_longer(-datetime, names_to = "pH", values_to = "value") %>%
  ggplot() +
  geom_point(aes(x = datetime, y = value, colour = pH), size = 0.15) +
  labs(title = "", x = "Time", y = expression(paste("p", H[T]))) +
  scale_color_manual(values=c("blue", "red"), 
                       name="",
                       breaks=c("pHint_tot_sf", "ph_dur_corr"),
                       labels=c("SeaFET", "Durafet")) +
  Mytheme(size_labs = 8)
print(ts_ph)

ggsave(filename = "figures/ts_ph.png")

>>>>

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("robfilter")) install.packages("robfilter")
if (!require("robfilter")) install.packages("robfilter")
library("robfilter")
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("reshape2")) install.packages("reshape2")
library("reshape2")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("lmtest")) install.packages("lmtest")
library("lmtest")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("seismicRoll")) install.packages("seismicRoll")
library("seismicRoll")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("cowplot")) install.packages("cowplot")
library(cowplot)
if (!require("htmlwidgets")) install.packages("htmlwidgets")
library("htmlwidgets")
if (!require("hms")) install.packages("hms")
library("hms")
knitr::opts_chunk$set(echo = TRUE)

@@

```{r figures for ESSD paper, echo=FALSE, message= FALSE, warning=FALSE}
Mytheme <- function(size_labs = 6, face_font="plain", ...) {
  theme_bw() +
  theme(
    # axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
    #     axis.title.x = element_text(face="plain", size=size_labs, margin=margin(0,0,0,0,"pt")),
    #     axis.text.y = element_text(face=face_font, color="black", size=size_labs),
    axis.text.x = element_blank(),
    #     axis.title.y = element_text(face="plain", size=size_labs),
    #     axis.ticks.x = element_line(size=0.1),
    #     axis.ticks.y = element_line(size=0.1),
    #     axis.ticks.length = unit(1.1, "mm"),
    #     panel.grid.major = element_line(size = 0.2, color="black", linetype="dotted"),
    #     aspect.ratio = 1 / 3,
        plot.margin = margin(t = 0, r = 0.3, b = 0, l = 0.3, unit = "cm")
  )
}
xlim <- c(as.POSIXct("2015-07-01 00:00:00"), as.POSIXct("2020-07-01 00:00:00"))
# select time series data
d <- as_tibble(d_all) %>%
  dplyr::select(datetime, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, ph_dur_corr, at_calc)
# time series temp
ts_temp <- d %>%
  dplyr::filter(!is.na(temp_insitu_11m)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = temp_insitu_11m), col = "blue", size = 0.15) +
  labs(title = "", x = "", y = "Temp. 11 m (°C)") +
  Mytheme(size_labs = 8)
print(ts_temp) 
# time series sal
ts_sal <- d %>%
  dplyr::filter(!is.na(sal_mix)) %>% 
ggplot() +
  geom_point(aes(x = datetime, y = sal_mix), col = "blue", size = 0.15) + 
  labs(title = "", x = "", y = "Salinity") +
  Mytheme(size_labs = 8)
print(ts_sal) 
# time series pco2
ts_pco2 <- d %>%
  dplyr::filter(!is.na(pco2_corr)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = pco2_corr), col = "blue", size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "", x = "", y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
  Mytheme(size_labs = 8)
print(ts_pco2) 
# time series pH
ts_ph <- d %>%
  dplyr::select(datetime, pHint_tot_sf, ph_dur_corr) %>%
  dplyr::filter(!is.na(pHint_tot_sf)) %>%
  pivot_longer(-datetime, names_to = "pH", values_to = "value") %>%
  ggplot() +
  geom_point(aes(x = datetime, y = value, colour = pH), size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "",
       x = "",
       y = expression(paste("p", H[T]))) +
  # scale_color_manual(
  #   values = c("blue", "red"),
  #   name = "",
  #   breaks = c("pHint_tot_sf", "ph_dur_corr"),
  #   labels = c("SeaFET", "Durafet")
  # ) +
  annotate(
    geom = "text",
    x = as.POSIXct("2018-06-01"),
    y = 8.35,
    label = "seaFET",
    color = "blue", size = 2
  ) +
  annotate(
    geom = "text",
    x = as.POSIXct("2018-06-01"),
    y = 8.25,
    label = "Durafet",
    color = "red", size = 2
  ) +
  Mytheme(size_labs = 8) +
  theme(legend.position = "none")
print(ts_ph) 
# time series AT
ts_at <- d %>%
  dplyr::filter(!is.na(at_calc)) %>% 
  ggplot() +
  geom_point(aes(x = datetime, y = at_calc), col = "blue", size = 0.15) +
  scale_x_datetime(limits = xlim) +
  labs(title = "", x = "Time", y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
  Mytheme(size_labs = 8) +
  theme(axis.title.x = element_text(face="plain", size=8))
print(ts_at)

#assemble time-series figure
cp <- cowplot::plot_grid(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, 
                   align = "v",
                   #labels = "AUTO",
                   ncol = 1
                   #width = 18,
                   #units = "cm"
                   )
print(cp)
cowplot::ggsave2(filename = "figures/ts_gg.png", plot = cp, height = 20, units = "cm")

ts_sal / ts_temp / ts_at
grid.arrange(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ncol = 1)
cowplot::save_plot(filename = "figures/ts_sp.pdf", plot = cp)
multiplot(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, cols = 1)
```
